Early Observations of \abc:\\ \textbf{a Type Ia Supernova Featuring Either} Strong Ejecta Mixing and/or Interaction with Diffuse Material

### 2017-10-30 doc/ms.tex
Update uncertainty estimates on median light curves

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.48\textwidth]{Branch_vel_evol.pdf}
  \caption{\textbf{Velocity evolution of \ion{Si}{2},   
           $v_{\mathrm{Is\,II}\,\lambda6355}$, for \abc\ compared to the median
           evolution of the four spectroscopic subclasses defined in
           \citet{2006PASP..118..560B}, using data from
           \citet{2012AJ....143..126B}. Typical uncertainties for \abc\ are
           $\sim$1000\,km\,s$^{-1}$ before $T_{B,\mathrm{max}}$, when the
           \ion{Si}{2}$\,\lambda6355$ profile is shallow and the minimum of
           absorption is difficult to determine, and $\sim$300\,km\,s$^{-1}$
           after $T_{B,\mathrm{max}}$. For the median curves, the typical
           scatter, determined via the interquartile range of the sample, is
           XXX $\sim$200\,km\,s$^{-1}$ XXX, around $T_{B,\mathrm{max}}$.
           At early times, core-normal and broad-line SNe have significantly
           faster \ion{Si}{2} than \abc, while the declining trend of coolSNe
           does not match \abc.}
  }
  \label{fig:branch_vel}
\end{figure}

@@

To determine the best fit parameters, we search a large grid over $t_0$,
$\alpha$, and the proportionality constant, and minimize $\chi^2$. The
modeling results show that the SN flux rises approximately linearly between
$t=-18\,\textrm{d}$ and $t=-15\,\textrm{d}$. Figure \ref{fig:early_lc_fit}
shows the best-fit result and the joint marginal distribution of $t_0$ and
$\alpha$. From the best-fit model we obtain $\alpha=0.98 \pm ^{0.16}_{0.14}$
and $t_0=-17.91 \pm ^{0.07}_{0.15}$ d, where the uncertainties represent the
marginalized 95\% confidence intervals \textit{THIS IS NOT THE CORRECT MARGINALIZED UNCERTAINTY}. Our first detection of \abc\ occurred
$\sim$${0.15}\,\textrm{d}$ after the SN first light. In the analysis that
follows, the precise values of the best-fit parameters are not important. The
critical finding here is that $\alpha \approx 1$ and $t_0 \approx -18 \,
\mathrm{d}$.

>>>>

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.48\textwidth]{Branch_vel_evol.pdf}
  \caption{\textbf{Velocity evolution of \ion{Si}{2},   
           $v_{\mathrm{Is\,II}\,\lambda6355}$, for \abc\ compared to the median
           evolution of the four spectroscopic subclasses defined in
           \citet{2006PASP..118..560B}, using data from
           \citet{2012AJ....143..126B}. Typical uncertainties for \abc\ are
           $\sim$1000\,km\,s$^{-1}$ before $T_{B,\mathrm{max}}$, when the
           \ion{Si}{2}$\,\lambda6355$ profile is shallow and the minimum of
           absorption is difficult to determine, and $\sim$300\,km\,s$^{-1}$
           after $T_{B,\mathrm{max}}$. For the median curves, the typical
           scatter, determined via the interquartile range of the sample, is
           $\sim$700\,km\,s$^{-1}$, around $T_{B,\mathrm{max}}$.
           At early times, core-normal and broad-line SNe have significantly
           faster \ion{Si}{2} than \abc, while the declining trend of coolSNe
           does not match \abc.}
  }
  \label{fig:branch_vel}
\end{figure}

@@

To determine the best fit parameters, we search a large grid over $t_0$,
$\alpha$, and the proportionality constant, and minimize $\chi^2$. The
modeling results show that the SN flux rises approximately linearly between
$t=-18\,\textrm{d}$ and $t=-15\,\textrm{d}$. Figure \ref{fig:early_lc_fit}
shows the best-fit result and the joint marginal distribution of $t_0$ and
$\alpha$. From the best-fit model we obtain $\alpha=0.98 \pm ^{0.16}_{0.14}$
and $t_0=-17.91 \pm ^{0.07}_{0.15}$ d, where the uncertainties represent the
marginalized 95\% confidence intervals. Our first detection of \abc\ occurred
$\sim$${0.15}\,\textrm{d}$ after the SN first light. In the analysis that
follows, the precise values of the best-fit parameters are not important. The
critical finding here is that $\alpha \approx 1$ and $t_0 \approx -18 \,
\mathrm{d}$.
